---
title: "Synodos - NCATS monotherapy data analysis"
output: html_document
---



```{r setup, include=FALSE}
library(data.table)
library(gdata)
library(plyr)
library(dplyr)
library(synapseClient)
library(ggplot2)
library(reshape2)
library("pheatmap")

source("~/dev/apRs/dataExploration_plots.R")
source("~/dev/apRs/plotting_helpers.R")
source("~/dev/apRs/expression_heatmap.R")

synapseLogin()
knitr::opts_chunk$set(warning = F, echo=F, message = F,
                      fig.align="center")
```


```{r}
#download data
NCATS_monotherapy_data_synid <- 'syn5816995'
drugScreen <- read.xls(synGet(NCATS_monotherapy_data_synid)@filePath, as.is=T)
colnames(drugScreen) <- gsub('\\.','',colnames(drugScreen))
drugs <- drugScreen %>% select(SampleID, SampleName, GeneSymbol)
drugs <- drugs[!duplicated(drugs),]

crc <- drugScreen$CRC
drugScreen['CRC_class'] <- 'inconclusive'
drugScreen$CRC_class[crc %in% c(1.1, 1.2, 2.1, 2.2)] <- 'Enhances'
drugScreen$CRC_class[crc %in% c(-1.1, -1.2, -2.1, -2.2)] <- 'Inhibits'
drugScreen$CRC_class[crc == 4] <- 'Inactive'

drugScreen$NF2status <- revalue(factor(drugScreen$NF2status),
                                replace=c('NF2 null '='NF2--',
                                          'NF2 expressing '='NF2++'))
```

#### DrugScreen metrics 

A.) Density Histograms Plots - AUC, AC50 & MaxResp

```{r fig.width=8, fig.height=4}
p1 <- ggplot(data=drugScreen, aes(x=AUC, fill=Cellline)) + geom_density(alpha=.7)
p1 <- p1 + theme_bw() + facet_grid(~CellType) 

p2 <- ggplot(data=drugScreen, aes(x=MaxResp, fill=Cellline)) + geom_density(alpha=.7)
p2 <- p2 + theme_bw() + facet_grid(~CellType) 

p3 <- ggplot(data=drugScreen, aes(x=AC50uM, fill=Cellline)) + geom_density(alpha=.7)
p3 <- p3 + theme_bw() + facet_grid(~CellType) 

multiplot(plotlist = list(p1,p2,p3), cols=2)
```


#### PCA (using AUC values)
```{r fig.width=4, fig.height=3 }
temp_d <- dcast(data=drugScreen, SampleID  ~ Cellline, value.var='AUC')
rownames(temp_d) <- temp_d[,1]
temp_d[,1] <- NULL
temp_d <- temp_d[complete.cases(temp_d),]
colorBy <- colnames(temp_d)
names(colorBy) <- colnames(temp_d)
m <- t(scale(temp_d))
doPCA(m, colorBy = colorBy)
```

#### Correlation plot
```{r fig.width=8, fig.height=6}
corPlot(temp_d)
```


#### Compare NCATS data with Synodos Drug Screen data
Using AUC as a metric for comparing the common drugs between the two datasets
```{r fig.width=8, fig.height=4}
MGH_lines <- fread(synGet('syn2773794')@filePath) %>% 
  select(cellLine,drug,trapezoid,IC50,maxEfficacy)
UCF_lines <- fread(synGet('syn2773891')@filePath) %>%
  select(cellLine,drug,trapezoid,IC50,maxEfficacy)
synodos_drugscreen_data <- rbind(MGH_lines, UCF_lines) %>% mutate(drug=factor(drug)) %>% mutate(drug = revalue(drug,replace=c('CUDC907'='CUDC-907','AR42'='AR-42','AZD2014'='AZD-2014', 'GDC0941'='GDC-0941','GDC0980'='GDC-0980', 'OSU03012'='OSU-03012','GSK2126458'='GSK-2126458'))
)
synodos_drugscreen_data <- synodos_drugscreen_data %>% group_by(cellLine, drug) %>% summarise(trapezoid=mean(trapezoid), IC50=mean(IC50), maxEfficacy=mean(maxEfficacy))

common_cellLines <- intersect(drugScreen$Cellline ,synodos_drugscreen_data$cellLine)

comp_plots <- lapply(common_cellLines, function(selected_cellline){
  synodos_d = synodos_drugscreen_data %>% filter(cellLine == selected_cellline)
  NCATS_d = drugScreen %>% filter(Cellline == selected_cellline )
  data <- merge(synodos_d, NCATS_d, by.x='drug',by.y='SampleName', how="inner") %>% mutate(NCATS.AUC=AUC, Syn.AUC=trapezoid)
  p1 <- ggplot(data=data, aes(x=NCATS.AUC, y=Syn.AUC)) + geom_point() + theme_bw()
  to_keep <- !(is.na(data$NCATS.AUC) | is.na(data$Syn.AUC))
  p1 <- p1 +  ggtitle(paste(selected_cellline, ' Correlation ', round(cor(data$NCATS.AUC[to_keep],data$Syn.AUC[to_keep], method="spearman"),2)))
  p1
})

multiplot(plotlist = comp_plots, cols=2)
```





#### Compare Drug Target Classes
Targets that have >= 5 drugs present


```{r, fig.width=12, fig.height=5}
counts <- table(drugs %>% filter(GeneSymbol != '' ) %>% .$GeneSymbol)
selected_drug_targets <- names(counts)[counts >= 5]

target_enrichment <- function(cellLine1, cellLine2){
  ldply(selected_drug_targets, function(target){
                d1 <- drugScreen %>% filter(GeneSymbol == target & Cellline %in% cellLine1)
                d2 <- drugScreen %>% filter(GeneSymbol == target & Cellline %in% cellLine2)
                AUC.pval=NA
                tryCatch({AUC.pval <-  wilcox.test(d1$AUC,d2$AUC,na.rm=T )$p.value},
                         error=function(w){w})
                AC50.pval=NA
                tryCatch({AC50.pval <-  wilcox.test(d1$AC50uM,d2$AC50uM,na.rm=T )$p.value},
                          error=function(w){w})
                MaxResp.pval=NA
                tryCatch({MaxResp.pval<-  wilcox.test(d1$MaxResp,d2$MaxResp,na.rm=T)$p.value},
                          error=function(w){w})
                to_keep <- !(is.na(d1$AUC)|is.na(d2$AUC))
                AUC.log2FC <- log2(mean(d1$AUC[to_keep]/d2$AUC[to_keep]))
                to_keep <- !(is.na(d1$AC50uM)|is.na(d2$AC50uM))
                AC50.log2FC <- log2(mean(d1$AC50uM[to_keep]/d2$AC50uM[to_keep]))
                to_keep <- !(is.na(d1$MaxResp)|is.na(d2$MaxResp))
                MaxResp.log2FC <- log2(mean(d1$MaxResp[to_keep]/d2$MaxResp[to_keep]))
                res <- data.frame(cellLine1=cellLine1, cellLine2=cellLine2,
                           AUC.pval=AUC.pval, AC50.pval=AC50.pval,
                           MaxResp.pval=MaxResp.pval,
                           AUC.log2FC=AUC.log2FC,AC50.log2FC=AC50.log2FC,
                           MaxResp.log2FC=MaxResp.log2FC,target=target)
          
          })
}


plotTargetEnrichment <- function(res, cellLine1, cellLine2){
    p1 <- ggplot(data=res, aes(y=-log10(AUC.pval), x=AUC.log2FC)) + geom_point() + theme_bw() + theme(legend.position="none")
    p1 <- p1 + geom_hline(aes(yintercept=-log10(.10), color="darkred")) 
    p1 <- p1 + geom_text( data = res %>% filter(AUC.pval <= .05), aes(y=-log10(AUC.pval)+.1, x=AUC.log2FC,label=target), size=2, color="#2c7fb8") +ggtitle(paste0(cellLine1,'-',cellLine2))
    p1 <- p1 + geom_text( data = res %>% filter(AUC.pval >= .05 & abs(AUC.log2FC) > .3), aes(y=-log10(AUC.pval)+.1, x=AUC.log2FC,label=target), size=3, color="#2c7fb8")
    
    # p2 <- ggplot(data=res, aes(y=-log10(AC50.pval), x=AC50.log2FC)) + geom_point() + theme_bw() +  theme(legend.position="none")
    # p2 <- p2 + geom_hline(aes(yintercept=-log10(.10)), color="darkred")
    # p2 <- p2 + geom_text( data = res %>% filter(AC50.pval <= .05), aes(y=-log10(AC50.pval)+.1, x=AC50.log2FC,label=target), size=2, color="#2c7fb8") +  ggtitle(paste0(cellLine1,'-',cellLine2))
    # p2 <- p2 + geom_text( data = res %>% filter(AC50.pval >= .05 & abs(AC50.log2FC) > 4), aes(y=-log10(AC50.pval)+.1, x=AC50.log2FC,label=target), size=2.5, color="#2c7fb8")
    #multiplot(plotlist=list(p1,p2), cols=2) 
    p1
}

HS01_vs_HS12 <- target_enrichment('HS01', 'HS12')
p1 <- plotTargetEnrichment(HS01_vs_HS12,'HS01','HS12')

Syn5_vs_Syn1 <- target_enrichment('Syn5', 'Syn1')
p2 <- plotTargetEnrichment(Syn5_vs_Syn1,'Syn5', 'Syn1')

Syn6_vs_Syn1 <- target_enrichment('Syn6', 'Syn1')
p3 <- plotTargetEnrichment(Syn6_vs_Syn1,'Syn6', 'Syn1')

multiplot(plotlist = list(p1,p2,p3), cols=3)
```



#### Sample Enrichment Plot - Drugs targeting AURKA
```{r}
d1 <- drugScreen %>% filter(GeneSymbol == 'AURKA' & Cellline %in% c('Syn5','Syn1', 'HS01', 'HS12') )
new_levels <- ddply(.data=d1, .variables = c('SampleName'), function(x) mean(x$AC50uM, na.rm = T)) %>% arrange(desc(V1)) %>% .$SampleName

ggplot(data=d1, aes(x=factor(SampleName, levels=new_levels), color=Cellline, y=AC50uM)) + geom_point() + facet_wrap(~ CellType, ncol=1) + theme_bw() + ggtitle('NCATS - AC50(uM) AURKA targetting drugs') + xlab('AURKA targetting drugs') + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



#### Tabluted form - NULL vs WT foldchange & significance
```{r enrichment, echo=F}
NCATS_enrichment_data <- rbind(HS01_vs_HS12, Syn6_vs_Syn1, Syn5_vs_Syn1)
NCATS_enrichment_data <- NCATS_enrichment_data %>% mutate(MaxResp.log2FC=signif(MaxResp.log2FC, digits=2),
                           AC50.log2FC=signif(AC50.log2FC, digits=2),
                           AUC.log2FC=signif(AUC.log2FC, digits=2),
                           MaxResp.pval=signif(MaxResp.pval, digits=2),
                           AC50.pval =signif(AC50.pval , digits=2),
                           AUC.pval=signif(AUC.pval, digits=2),
                           NULL_line = cellLine1,
                           WT_line = cellLine2, Target = target) %>%
  select(Target, NULL_line, WT_line,AC50.log2FC,AUC.log2FC,MaxResp.log2FC,MaxResp.pval,AC50.pval,AUC.pval)
DT::datatable(NCATS_enrichment_data, filter='top')

#UPLOAD Data to synapse
write.table(NCATS_enrichment_data, file="NCATS_target_enrichment.tsv", sep="\t", col.names = T,
            row.names = F, quote = F)

synStore(File("NCATS_target_enrichment.tsv", parentId = "syn2773788"),
         used = NCATS_monotherapy_data_synid,
         executed = "")




```




### Comparing Drug Response NF2 NULL vs WT
```{r, echo=F, fig.width=10}
#NF2++ vs NF2--
fit <- lm(AUC ~ NF2status + SampleID, data=drugScreen)
lm.summary <- summary(fit)
lm.coef <- data.frame(coef(lm.summary))
colnames(lm.coef) <- c('estimate', 'stdError', 't.val', 'p.val')
lm.coef['SampleID'] <- gsub('SampleID' ,'',rownames(lm.coef))
lm.coef <- lm.coef %>% arrange(p.val)
selected_compounds <- lm.coef$SampleID[1:60]
temp_d <- dcast(data=drugScreen %>% filter(SampleID %in% selected_compounds),
                SampleName ~ Cellline, value.var='AUC')
rownames(temp_d) <- temp_d$SampleName
temp_d$SampleName <- NULL
temp_d <- temp_d[complete.cases(temp_d),]
pheatmap(scale(t(temp_d)),cellwidth=10,cellheight=10,fontsize_row=10 )
pheatmap(t(temp_d),cellwidth=10,cellheight=10)
```



### Comparing Drugs Across Schwannoma - NULL / WT 
```{r schwannoma, echo=F, fig.width=10, fig.height=5, eval=F}
#schwannoma data
schwannoma <- drugScreen %>% filter(Cellline %in% c('HS01', 'HS12', 'MS02'))
schwannoma_human <- drugScreen %>% filter(Cellline %in% c('HS01', 'HS12'))
#Schwannoma
schwannoma_human$Cellline <- factor(schwannoma_human$Cellline, level=c('HS12','HS01'))
```


