---
title: "NCATS Single Agent Analysis"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
dyn.load('/Library/Java/JavaVirtualMachines/jdk1.8.0_131.jdk/Contents/Home/jre/lib/server/libjvm.dylib') ##rjava will not load upon knit otherwise
library(plyr)
library(tidyverse)
library(ggrepel)
library(parallel)
library(pheatmap)
library(synapseClient)
library(plotly)
library(DT)
source("NCATS_helpers.R")
synapseLogin()

map2<- read.table("ncats_drugs_curated.txt", sep = "\t", quote = "", comment.char = "", header = T)
ncats <-read.table(synGet("syn8314523")@filePath, header = T, sep = "\t")
targs <- read.table(synGet("syn11609839")@filePath, header = T, sep = "\t", comment.char = "", quote = "\"")

x<-synGet("syn11559906")@filePath
drugstruct<-read.table(x, sep = '\t', header = TRUE, comment.char = "", quote = "")

ncats$Cell.line <- as.character(ncats$Cell.line)
ncats$Cell.line[ncats$Cell.line=="HS12"] <- "HS11"
```
##Compare Maximum Response to AUC
```{r echo=FALSE, message=FALSE, warning=FALSE}

cor.metric <- cor.test(ncats$Max.Resp, ncats$AUC)

ncats$CRC <- as.factor(ncats$CRC)

ggplot(data = ncats)+
  geom_point(aes(x = Max.Resp, y=AUC, color = CRC)) +
  labs(title = paste0("Cor estimate = ", round(cor.metric$estimate,4)))

hist(ncats$CRC)

```

A comparison of maximum response vs AUC as the readout of drug efficacy indicates that while these metrics are generally well correlated (0.71) they are not identical in terms of distribution. Many molecules with a maximum response of ~0-20% cell viability still have very high AUCs, suggesting that the dose response curves for these molecules are only effective at higher concentrations. Others show high AUC and high maximum response suggesting these molecules are not effective at all.
AUC may better represent “viability” for this dataset. 

##Mapping drug target response (differential AUC) to logFC of gene at baseline

###Schwannoma

Plotting the mean differential response across matched pairs (HS01 vs HS11? Should this be HS11 in this dataset, the matched isogenic pair for HS01..?) to individual targets using the NCATS annotations for targets suggests that most targets with a mean differential response further from zero are closer to zero in terms of log FC. In other words, perhaps the more meaningful targets have a negligible logFC, suggesting that good drug targets might not be ones that are extremely highly differentially expressed? Meningioma seems similar, but notably most points are below 0 for differential response suggesting the NF2 null meningioma cells are in general more sensitive to drugs in this assay or with this readout (AUC). To account for this, I went back and centered the differential AUCs for both of the cell lines for this analysis.

```{r echo=FALSE, message=FALSE, warning=FALSE} 
##expression of drug targets vs 

####schwannoma 
ncats.null <- ncats %>% 
  select(Sample.ID, Cell.line, AUC) %>% 
  filter(Cell.line == "HS01") %>% 
  select(-Cell.line) %>% 
  dplyr::group_by(Sample.ID) %>% 
  dplyr::summarise(avgNull = mean(AUC))

ncats.wt <- ncats %>% 
  select(Sample.ID, Cell.line, AUC) %>% 
  filter(Cell.line == "HS11") %>% 
  select(-Cell.line) %>% 
  dplyr::group_by(Sample.ID) %>% 
  dplyr::summarise(avgWT = mean(AUC))

ncats.min <- full_join(ncats.null, ncats.wt) %>% 
  dplyr::mutate(diffr = avgNull - avgWT) %>% 
  magrittr::set_colnames(c("ncgc", "avgNull", "avgWT", "diffr")) %>% 
  dplyr::left_join(map2)

ncats.min$diffr <- as.vector(scale(ncats.min$diffr, scale = F, center = T))

sch.deg <- read.table(synGet("syn10881886")@filePath, header = T, sep = "\t") %>% 
  separate(geneName, c("ens","Hugo_Gene"), sep = "\\|") %>%
  filter(cellLine1 == "HS01", cellLine2 == "HS11", treatment1 == "DMSO", treatment2 == "DMSO")

ncats.mush <- ncats.min %>% left_join(targs) %>% 
  group_by(Hugo_Gene) %>%
  dplyr::summarize(mean = mean(diffr), sd = sd(diffr)) %>% 
  ungroup() %>% 
  inner_join(sch.deg)

ggplot(ncats.mush, aes(y = mean, x = logFC)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd), color = "black") +
  geom_label_repel(data = ncats.mush %>% filter(abs(mean>20) & abs(logFC > 1)), aes(label = Hugo_Gene)) +
  labs(x = "gene logFC", y = "mean differential response")

ggplot(ncats.mush, aes(y = mean, x = logFC)) +
  geom_point() +
  geom_label_repel(data = ncats.mush %>% filter(abs(mean)>20 & abs(logFC) > 1), aes(label = Hugo_Gene)) +
  labs(x = "gene logFC", y = "mean differential response")

ggplot(ncats.mush, aes(y = mean, x = logFC)) +
  geom_point() +
  geom_label_repel(data = ncats.mush %>% filter(abs(mean)>50), aes(label = Hugo_Gene)) +
  labs(x = "gene logFC", y = "mean differential response")

```



###Meningioma

```{r echo=FALSE, message=FALSE, warning=FALSE}
ncats.null <- ncats %>% 
  select(Sample.ID, Cell.line, AUC) %>% 
  filter(Cell.line == "Syn5") %>% 
  select(-Cell.line) %>% 
  dplyr::group_by(Sample.ID) %>% 
  dplyr::summarise(avgNull = mean(AUC))

ncats.wt <- ncats %>% 
  select(Sample.ID, Cell.line, AUC) %>% 
  filter(Cell.line == "Syn1") %>% 
  select(-Cell.line) %>% 
  dplyr::group_by(Sample.ID) %>% 
  dplyr::summarise(avgWT = mean(AUC))

ncats.min <- full_join(ncats.null, ncats.wt) %>% 
  dplyr::mutate(diffr = avgNull - avgWT) %>% 
  magrittr::set_colnames(c("ncgc", "avgNull", "avgWT", "diffr")) %>% 
  dplyr::left_join(map2) 

ncats.min$diffr <- as.vector(scale(ncats.min$diffr, scale = F, center = T))

men.deg <- read.table(synGet("syn10881885")@filePath, header = T, sep = "\t") %>% 
  separate(geneName, c("Hugo_Gene","ens"), sep = "\\|") %>%
  filter(cellLine1 == "Syn5", cellLine2 == "Syn1", treatment1 == "DMSO", treatment2 == "DMSO")

ncats.mush <- ncats.min %>% left_join(targs) %>% 
  group_by(Hugo_Gene) %>%
  dplyr::summarize(mean = mean(diffr), sd = sd(diffr)) %>% 
  ungroup() %>% 
  inner_join(men.deg)

ggplot(ncats.mush, aes(y = mean, x = logFC)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd), color = "black") +
  geom_label_repel(data = ncats.mush %>% filter(abs(mean)>20 & abs(logFC) > 1), aes(label = Hugo_Gene)) +
  labs(x = "gene logFC", y = "mean differential response")

ggplot(ncats.mush, aes(y = mean, x = logFC)) +
  geom_point() +
  geom_label_repel(data = ncats.mush %>% filter(abs(mean)>20 & abs(logFC) > 1), aes(label = Hugo_Gene)) +
  labs(x = "gene logFC", y = "mean differential response")

ggplot(ncats.mush, aes(y = mean, x = logFC)) +
  geom_point() +
  geom_label_repel(data = ncats.mush %>% filter(abs(mean)>50), aes(label = Hugo_Gene)) +
  labs(x = "gene logFC", y = "mean differential response")
```

##Clustering and heatmap of scaled AUC data for all cell lines

Unsupervised clustering/heatmapping of AUCs (first) and scaled AUCs (second) suggests that clustering is driven by Species (MS02 is mouse, remainder are human), followed by cell type (Syn1,5 are arachnoidal, Syn6 is arachnoidal cancer - meningioma, HS01-12 are Schwann cells). Interestingly, Syn5-6 are both NF2-null and cluster closely, while Syn1 is more distant, even though Syn5 and Syn1 are an isogenic pair.

```{r echo=FALSE, message=FALSE, warning=FALSE}

ncats.mat <- ncats %>% select(Cell.line, Sample.ID, AUC) %>% spread(Sample.ID, AUC) %>% remove_rownames()
rownames(ncats.mat) <- ncats.mat$Cell.line
ncats.mat <- select(ncats.mat, -Cell.line) %>% t()

pheatmap(ncats.mat)

ncats.mat.scale <- scale(ncats.mat)
pheatmap(ncats.mat.scale)

```

##PCA of drugs

PCA of all the AUC of drugs in all 6 cell lines shows that two primary groups of drug responses exist.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ncats.null <- ncats %>% 
  select(Sample.ID, Cell.line, AUC) %>% 
  filter(Cell.line %in% c("HS01","Syn5", "Syn6")) %>% 
  select(-Cell.line) %>% 
  dplyr::group_by(Sample.ID) %>% 
  dplyr::summarise(avgNull = mean(AUC))

ncats.wt <- ncats %>% 
  select(Sample.ID, Cell.line, AUC) %>% 
  filter(Cell.line %in% c("HS11","Syn1")) %>% 
  select(-Cell.line) %>% 
  dplyr::group_by(Sample.ID) %>% 
  dplyr::summarise(avgWT = mean(AUC))

ncats.min <- full_join(ncats.null, ncats.wt) %>% 
  dplyr::mutate(diffr = avgNull - avgWT) %>% 
  magrittr::set_colnames(c("ncgc", "avgNull", "avgWT", "diffr")) %>% 
  dplyr::left_join(map2)

pca<-prcomp(ncats.mat)

pca.df <- as.data.frame(pca$x) %>% rownames_to_column("ncgc") %>% left_join(ncats.min)

ggplot(data = pca.df) +
  geom_point(aes(x=PC1, y=PC2, color = diffr, label = drug_name)) +
  viridis::scale_color_viridis()

ggplotly(p = ggplot2::last_plot(), tooltip = c("x","y", "drug_name"))
  
plot_ly(pca.df, x = ~PC1, y = ~PC2, z = ~PC3, hovertext = ~drug_name, hoverinfo = ~drug_name, color = ~diffr) %>% 
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'PC1'),
                     yaxis = list(title = 'PC2'),
                     zaxis = list(title = 'PC3')))

datatable(ncats.min)
```

##PCA of cell lines

PCA of cell lines with drug AUCs shows that mouse and human clearly separate. HS01-HS11 are very close, as are Syn5-6. Syn1 is less close to Syn5 and Syn6 as was seen with hierarchical clustering. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

pca<-prcomp(t(ncats.mat))
pca.df <- as.data.frame(pca$x) %>% rownames_to_column("cellLine")

plot_ly(pca.df, x = ~PC1, y = ~PC2, z = ~PC3, hovertext = ~cellLine, hoverinfo = ~cellLine) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'PC1'),
                     yaxis = list(title = 'PC2'),
                     zaxis = list(title = 'PC3')))
```

##t-SNE of cell lines - this doesn't work so well.

tSNE of cell lines - doesn’t work well due to data - cannot change perplexity higher than 1 without the calculation failing. tSNE across drugs has been optimized in a different analysis. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(Rtsne.multicore)
##tSNE of cell lines --- this doesn't really work, because N of cell lines vs observations is too different, would not trust these results
tsne<-Rtsne.multicore(t(ncats.mat), perplexity = 1)
tsne.df <- as.data.frame(tsne$Y) %>% rownames_to_column("cellLine")

plot_ly(tsne.df, x = ~V1, y = ~V2, hovertext = ~cellLine, hoverinfo = ~cellLine) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'PC1'),
                     yaxis = list(title = 'PC2')))

```


##T-test all drugs - only on human cell lines

Comparison of ttests of AUC (NF2null vs NF2wt) and max response (same comparison) show little association between significance of one readout vs the other. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

ncats <- filter(ncats, Cell.line %in% c("HS01", "HS11", "Syn1", "Syn5", "Syn6"))

res<-mclapply(unique(ncats$Sample.ID), function(x){
  drugs.ncats <- ncats %>% filter(Sample.ID == x)
  null <- drugs.ncats %>% filter(NF2.status == "NF2 null ")
  wt <- drugs.ncats %>% filter(NF2.status == "NF2 expressing ")
  bar<-wilcox.test(wt$AUC, null$AUC)
  c(bar$statistic, "pval" = bar$p.value)
}, mc.cores = detectCores())

names(res) <- as.character(unique(ncats$Sample.ID))
drugs<-ldply(res)

res2<-mclapply(unique(ncats$Sample.ID), function(x){
  drugs.ncats <- ncats %>% dplyr::filter(Sample.ID == x)
  null <- drugs.ncats %>% filter(NF2.status == "NF2 null ")
  wt <- drugs.ncats %>% filter(NF2.status == "NF2 expressing ")
  bar<-wilcox.test(wt$Max.Resp, null$Max.Resp)
  c(bar$statistic, "pval" = bar$p.value)
}, mc.cores = detectCores())

names(res2) <- as.character(unique(ncats$Sample.ID))
drugs2<-ldply(res2) %>% set_names(c(".id", "t_maxresp","pval_maxresp"))

drugs3 <- full_join(drugs,drugs2)

ggplot(data = drugs3) +
  geom_point(aes(x=pval, y=pval_maxresp))

datatable(drugs3)
```

##Wilcox-test all targets and plot against mean differential AUC
#####mapping datasets to NCATS with 0.95 chemical similarity or greater == "same drug"
#####ranked AUCs
#####spearman correlation with BH corrected p value
#####might be driven a lot by missing dat


#####not shown here because the mapping takes very long time to knit

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
##sig test all targets
fp.evo <- readRDS("fpevo.rds")
evo <- readRDS("evotec_dgidb.rds")
evo <- evo %>% filter(N_quantitative > N_inactive | N_qualitative > N_inactive | N_DGIDB > 0)


targs <- mclapply(as.character(drugstruct$smiles2), function(x){
  x<- getSimMols(x, 0.95)
  
  if(nrow(x)>0){
    x
  }else{
    as.data.frame(c("NothingFound"))
  }
  }, mc.cores = detectCores())

names(targs) <- as.character(drugstruct$smiles2) 
targs<-ldply(targs)

map<- read.table(synGet("syn11591280")@filePath, sep = "\t", quote = "", comment.char = "", header = T) 
colnames(map)[3] <- ".id"
targs2 <- left_join(targs, map) %>% filter(`Tanimoto Similarity` > 0.99) %>% dplyr::select(-6)

targs2 <- targs2 %>% left_join(evo, by = "Original_molecule_SMILES")
summary <- as.data.frame(table(targs2$Hugo_Gene)) %>% filter(Freq >= 5)
targs3 <- filter(targs2, Hugo_Gene %in% summary$Var1)

res<-mclapply(unique(targs3$Hugo_Gene), function(x){
  foo <- targs3 %>% dplyr::filter(Hugo_Gene == x)
  drugs.ncats <- ncats %>% filter(Sample.ID %in% foo$ncgc)
  null <- drugs.ncats %>% filter(Cell.line %in% c("HS01","Syn5"))
  wt <- drugs.ncats %>% filter(Cell.line %in% c("HS11","Syn6"))
  bar<-wilcox.test(wt$AUC, null$AUC)
  diff <- mean(wt$AUC) - mean(null$AUC)
  c(bar$statistic, "pval" = bar$p.value, "diff" = diff)
  
}, mc.cores = detectCores())

names(res) <- unique(targs3$Hugo_Gene)
res <- ldply(res)
res$bh <- p.adjust(res$pval, method = "BH")

#targs4 <- dplyr::select(targs3, .id, Common_Name.x, Original_molecule_SMILES, `Tanimoto Similarity`, ncgc, Hugo_Gene) %>%
#   add_column("true" = rep(TRUE, nrow(targs3))) %>% 
#   distinct() %>%
#   spread(Hugo_Gene, "true", fill = FALSE)



p<-ggplot(data = res) +
  geom_point(aes(x=diff, y=-bh, color = bh < 0.05)) +
  geom_label_repel(data = res %>% filter(bh <0.05, abs(diff)>30), aes(x=diff, y=-bh, label = .id))

DT::datatable(res)
```

##Drug response correlation to CCLE/Sanger

Mapped overlapping drugs using structures to CTRP and Sanger datasets (200-300 overlapping drugs), and then ranked the AUCs to normalize across datasets. Then tested correlation for all 6 cell lines to the remaining cell lines across both datasets. Enriched for positively correlated, no significantly negatively correlated cell lines from CTRP or Sanger. Generally most highly correlated to the cell lines from the same screen (to be expected) but several other highly correlated cell lines are present. Unfortunately no meningiomas or schwannomas in these data. Some cell lines that are labeled here are neurological cancers but there is a mixture of other cancer types too. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

getSimMolsFlex <- function(input, sim.thres, comp.fingerprints) {
  input <- input
  fp.inp <- parseInputFingerprint(input)
  
  sims <- mclapply(fp.inp, function(i) {
    sim <- sapply(comp.fingerprints, function(j) {
      distance(i, j)
    })
    bar <- as.data.frame(sim)
    bar$match <- rownames(bar)
    bar
  }, mc.cores = detectCores())
  sims <- ldply(sims)
  sims2 <- sims %>% filter(sim >= sim.thres) %>% arrange(-sim)
  sims2
}

ctrp.map <- lapply(as.character(drugstruct$smiles2), function(x){

  x<- getSimMolsFlex(x, 0.95, fp.ctrp)
  
  if(nrow(x)>0){
    x
  }else{
    c("Nothing Found")
  }
  })

names(ctrp.map) <- as.character(drugstruct$smiles2) 
ctrp.filt <- ctrp.map[ctrp.map != "Nothing Found"]
ctrp.filt <- ldply(ctrp.filt)
ctrp.filt <- set_names(ctrp.filt, c("smiles2", "sim", "cpd_smiles"))

ctrp.join <- inner_join(ctrp.filt, drugstruct) %>% inner_join(ncats, by = c("ncgc" = "Sample.ID")) %>% select(ncgc, cpd_smiles, Cell.line, AUC) %>% group_by(ncgc, cpd_smiles, Cell.line) %>% dplyr::summarize(mAUC = mean(AUC)) %>% ungroup() %>% spread(Cell.line, mAUC)
drug.resp2 <- t(drug.resp) %>% as.data.frame() %>% rownames_to_column("cpd_name") %>% inner_join(ctrp.structures)  
ctrp.join2 <- select(ctrp.join, ncgc, cpd_smiles) %>% distinct() %>% inner_join(drug.resp2) %>% select(1,3:890) %>%
  inner_join(ctrp.join) %>% select(1,3:889,891:895) %>% dplyr::mutate_at(vars(-ncgc), funs(rank(-.)))


plotCors <- function(cellLine, input_df, label.threshold){
  
  df <- sapply(colnames(input_df)[2:length(colnames(input_df))], function(x){
         foo<-cor.test(input_df[[cellLine]], input_df[[x]])
         bar <- c("pval" = foo$p.value, foo$estimate)
  })
  
  df <- t(df) %>% as.data.frame() %>% rownames_to_column("cellLine")
  df$bh <- p.adjust(df$pval, method = "BH")
  df$label <- ""
  df$label[df$bh<=label.threshold] <- df$cellLine[df$bh<=label.threshold]
  
  DT::datatable(df)
  
  ggplot(df) +
    geom_point(aes(x = cor, y = -bh)) +
    geom_label_repel(aes(x = cor, y = bh, label = label))
  
  
}

```

####HS01 correlation to CTRP
```{r echo=FALSE, message=FALSE, warning=FALSE}
plotCors("HS01", ctrp.join2, 5e-13) #null
```

####HS11 correlation to CTRP

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotCors("HS11", ctrp.join2, 5e-13) #wt
```

####Syn1 correlation to CTRP

```{r echo=FALSE, message=FALSE, warning=FALSE}

plotCors("Syn1", ctrp.join2, 5e-13) #wt
```

####Syn5 correlation to CTRP

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotCors("Syn5", ctrp.join2, 5e-13) #null
```

####Syn6 correlation to CTRP

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotCors("Syn6", ctrp.join2, 5e-13) #null

```


```{r echo=FALSE, message=FALSE, warning=FALSE}                     
sang.map <- lapply(as.character(drugstruct$smiles2), function(x){
  x<- getSimMolsFlex(x, 0.95, fp.sang)
  
  if(nrow(x)>0){
    x
  }else{
    c("Nothing Found")
  }
  })

names(sang.map) <- as.character(drugstruct$smiles2) 
sang.filt <- sang.map[sang.map != "Nothing Found"]
sang.filt <- ldply(sang.filt)
sang.filt <- set_names(sang.filt, c("smiles2", "sim", "smiles"))

cell.deets <- read.table(synGet("syn9988099")@filePath, sep = "\t", header = TRUE)
cell.deets$cellLine <- as.character(cell.deets$COSMIC_ID)
mini.deets <- cell.deets %>% select(Sample.Name, cellLine)

drug.resp.sang.test <- as.data.frame(drug.resp.sang) %>% 
  rownames_to_column("cellLine") %>% 
  left_join(mini.deets) %>% 
  select(-cellLine) %>% 
  gather("drug", "auc", -Sample.Name) %>% 
  group_by(Sample.Name, drug) %>% 
  dplyr::summarize(auc = mean(auc, na.rm = T)) %>% 
  ungroup() %>% 
  filter(!is.na(Sample.Name)) %>% 
  spread(drug, auc) %>% 
  remove_rownames() %>% 
  column_to_rownames("Sample.Name")

sang.join <- inner_join(sang.filt, drugstruct) %>% inner_join(ncats, by = c("ncgc" = "Sample.ID")) %>% select(ncgc, smiles, Cell.line, AUC) %>% group_by(ncgc, smiles, Cell.line) %>% dplyr::summarize(mAUC = mean(AUC)) %>% ungroup() %>% spread(Cell.line, mAUC)
drug.resp2 <- t(drug.resp.sang.test) %>% as.data.frame() %>% rownames_to_column("sanger_names") %>% inner_join(sang.structures)  
sang.join2 <- select(sang.join, ncgc, smiles) %>% distinct() %>% inner_join(drug.resp2) %>% select(1,4:993) %>%
  inner_join(sang.join) %>% select(-992) %>% dplyr::mutate_at(vars(-ncgc), funs(rank(-.)))
```

####HS01 correlation to Sanger

```{r echo=FALSE, message=FALSE, warning=FALSE}

plotCors("HS01", sang.join2, 5e-13) #null
```

####HS11 correlation to Sanger

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotCors("HS11", sang.join2, 5e-13) #wt
```

####Syn1 correlation to Sanger

```{r echo=FALSE, message=FALSE, warning=FALSE}

plotCors("Syn1", sang.join2, 5e-13) #wt
```

####Syn5 correlation to Sanger

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotCors("Syn5", sang.join2, 5e-13) #null
```

####Syn6 correlation to Sanger

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotCors("Syn6", sang.join2, 5e-13) #null

```

Should search to see if these are NF2 mutant or low expressing cell lines… an integrated correlative analysis would be interesting, plotting drug response correlation to mutation correlation (T/F) or expression correlation (ranked gene list)…correlation of correlations?
```{r}
targs4 <- read.table(synGet("syn11609840")@filePath,header = T) %>%
  dplyr::select(-1,-2,-3,-4) %>% distinct()

jaccard_targs <- mclapply(targs4$ncgc, function(x){
  a <- targs4[targs4$ncgc==x,]
  genes_a <- colnames(a)[a==TRUE]
  sapply(targs4$ncgc, function(y){
      b <- targs4[targs4$ncgc==y,]
      genes_b <- colnames(b)[b==TRUE]
      jaccard <- length(intersect(genes_a,genes_b))/length(union(genes_a, genes_b))
  })
}, mc.cores = detectCores())

```
```{r}
# library(diffusr)
# 
# map <- read.table(synGet("syn11559906")@filePath, sep = "\t", header = T, comment.char = "", quote = "")
# 
# fp <- parseInputFingerprint(as.character(map$smiles2))
# 
# sim <- fp.sim.matrix(fp)
# 
# sim.filt <- sim
# sim.filt[sim.filt<0.5] <- 0
# sim.net <- sim.filt
# 
# diffs2 <- ncats.min$diffr 
# names(diffs2) <- ncats.min$ncgc
# diffs2[diffs2 > 0] <- 0
# diffs2 <- abs(diffs2)
# diffs2 <- diffs2/sum(diffs2) 
# 
# pt    <- random.walk(diffs2, sim.net, niter = 10000)
# rownames(pt) <- names(diffs2)
```

