---
title: "NCATS Report"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---


```{r, include=FALSE}
library(synapseClient)
library(ggplot2)
library(dplyr)
library(viridis)
library(tidyr)
library(purrr)
synapseLogin()
```

```{r, include=FALSE}
x<-synGet("syn8314523")@filePath
drugdat<-read.table(x, sep = '\t', header = TRUE, fill = TRUE)

colnames(drugdat) <- c('Protocol.Name', 'Sample.ID', 'Cell.Line', 'Cell.Type', 
                       'NF2.Status', 'AC50.uM', 'CRC', 'Max.Resp', 'Log.AC50.uM', 
                       'Compound.Name', 'AUC', 'AUC.Fit', 'Gene.Name')
```

##Max Response colored by selectivity for NF2 -/-. Yellow points are more selective drugs. Labeled drugs have a 4-fold or greater max response in the plotted NF2 mutant cell line as compared to NF2 wild-type.

```{r, echo=FALSE, fig.width=6}
sub<-select(drugdat, Cell.Line, Max.Resp, Compound.Name)

sub2 <- sub %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, Max.Resp)
    })) %>% 
  unnest(data)

ggplot(sub2, aes(x= HS01, y=HS12)) +
    geom_point(stat = "identity", aes(color=(HS01/HS12))) + 
    coord_fixed() +
    scale_color_viridis() +
    geom_text(data=subset(sub2, HS01/HS12>=4), aes(label = Compound.Name), size = 2)

ggsave("HS01_HS12_MaxResponse_Selectivity.png", height = 6, width = 6)

ggplot(sub2, aes(x= MS02, y=HS12)) +
  geom_point(stat = "identity", aes(color=(MS02/HS12))) + 
  coord_fixed() +
  scale_color_viridis() +
  geom_text(data=subset(sub2, MS02/HS12>=4), aes(label = Compound.Name), size = 2)

ggsave("MS02_HS12_MaxResponse_Selectivity.png", height = 6, width = 6)

ggplot(sub2, aes(x= Syn5, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn5/Syn1))) + 
  coord_fixed() +
  scale_color_viridis() +
  geom_text(data=subset(sub2, Syn5/Syn1>=4), aes(label = Compound.Name), size = 2)

ggsave("Syn5_Syn1_MaxResponse_Selectivity.png", height = 6, width = 6)

ggplot(sub2, aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn6/Syn1))) + 
  coord_fixed() +
  scale_color_viridis() +
  geom_text(data=subset(sub2, Syn6/Syn1>=4), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_MaxResponse_Selectivity.png", height = 6, width = 6)


```

##AUC colored by selectivity for NF2 -/-. Yellow points are more selective drugs. Labeled drugs have a 1.5-fold or greater difference in AUC in the plotted NF2 mutant cell line as compared to NF2 wild-type (lower AUC in NF2 mutant cell line).

```{r, echo=FALSE, fig.width=6}
sub3 <- select(drugdat, Cell.Line, AUC, Compound.Name)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, AUC)
  })) %>% 
  unnest(data)

ggplot(sub4, aes(x= HS01, y=HS12)) +
  geom_point(stat = "identity", aes(color=(HS12/HS01))) + 
  coord_fixed() +
  scale_color_viridis(option = "A") +
  geom_text(data=subset(sub4, HS12/HS01>=1.5), aes(label = Compound.Name), size = 2)

ggsave("HS01_HS12_AUC_Selectivity.png", height = 6, width = 6)

ggplot(sub4, aes(x= MS02, y=HS12)) +
  geom_point(stat = "identity", aes(color=(HS12/MS02))) + 
  coord_fixed() +
  scale_color_viridis(option = "A") +
  geom_text(data=subset(sub4, HS12/MS02>=1.5), aes(label = Compound.Name), size = 2)

ggsave("MS02_HS12_AUC_Selectivity.png", height = 6, width = 6)

ggplot(sub4, aes(x= Syn5, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn1/Syn5))) + 
  coord_fixed() +
  scale_color_viridis(option = "A") +
  geom_text(data=subset(sub4, Syn1/Syn5>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn5_Syn1_AUC_Selectivity.png", height = 6, width = 6)

ggplot(sub4, aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn1/Syn6))) + 
  coord_fixed() +
  scale_color_viridis(option = "A") +
  geom_text(data=subset(sub4, Syn1/Syn6>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_AUC_Selectivity.png", height = 6, width = 6)

ggplot(sub4, aes(x= HS01, y=HS12)) +
  geom_point(stat = "identity", aes(color=(HS12/HS01))) + 
  scale_color_viridis(name = "Selectivity", option = "C") +
  labs(title="Schwannoma", x="NF2 deficient", y="NF2 normal") +
  coord_fixed() +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_cartesian(xlim = c(0, 650), ylim = c(0, 650))

ggsave("HS01_HS12_AUC_Selectivity_nolab.png", height = 6, width = 6)

ggplot(sub4, aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn1/Syn6))) + 
  scale_color_viridis(name = "Selectivity", option = "C") +
  labs(title="Meningioma", x="NF2 deficient", y="NF2 normal") +
  coord_fixed() +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_cartesian(xlim = c(0, 650), ylim = c(0, 650))
     
ggsave("Syn6_Syn1_AUC_Selectivity_nolab.png", height = 6, width = 6)
```

##Maximum response colored by average potency. Yellow points are more potent drugs (average of measurements for both cell lines plotted). Labeled drugs have a an average maximum response of 99% or greater for the plotted cell lines. 

```{r, echo=FALSE, fig.width=6}
ggplot(sub2, aes(x= HS01, y=HS12)) +
  geom_point(stat = "identity", aes(color=(HS12+HS01)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = , option = "B") +
  geom_text(data=subset(sub2, ((HS01+HS12)/2)>=99), aes(label = Compound.Name), size = 2)

ggsave("HS01_HS12_MaxResponse_AvgPotency.png", height = 6, width = 6)

ggplot(sub2, aes(x= MS02, y=HS12)) +
  geom_point(stat = "identity", aes(color=(HS12+MS02)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = , option = "B") +
  geom_text(data=subset(sub2, ((MS02+HS12)/2)>=99), aes(label = Compound.Name), size = 2)

ggsave("MS02_HS12_MaxResponse_AvgPotency.png", height = 6, width = 6)

ggplot(sub2, aes(x= Syn5, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn1+Syn5)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = , option = "B") +
  geom_text(data=subset(sub2, ((Syn1+Syn5)/2)>=99), aes(label = Compound.Name), size = 2)

ggsave("Syn5_Syn1_MaxResponse_AvgPotency.png", height = 6, width = 6)

ggplot(sub2, aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn1+Syn6)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = , option = "B") +
  geom_text(data=subset(sub2, ((Syn1+Syn6)/2)>=99), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_MaxResponse_AvgPotency.png", height = 6, width = 6)

```

##AUC, colored by average potency. Yellow points are more potent drugs (average of measurements for both cell lines plotted). Labeled drugs have an average AUC of 250 or less for both plotted lines. 

```{r, echo=FALSE, fig.width=6}
sub3 <- select(drugdat, Cell.Line, AUC, Compound.Name)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, AUC)
  })) %>% 
  unnest(data)

ggplot(sub4, aes(x= HS01, y=HS12)) +
  geom_point(stat = "identity", aes(color=(HS12+HS01)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = -1, option = "C") +
  geom_text(data=subset(sub4, ((HS01+HS12)/2)<=250), aes(label = Compound.Name), size = 2)

ggsave("HS01_HS12_AUC_AvgPotency.png", height = 6, width = 6)

ggplot(sub4, aes(x= MS02, y=HS12)) +
  geom_point(stat = "identity", aes(color=(HS12+MS02)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = -1, option = "C") +
  geom_text(data=subset(sub4, ((MS02+HS12)/2)<=250), aes(label = Compound.Name), size = 2)

ggsave("MS02_HS12_AUC_AvgPotency.png", height = 6, width = 6)

ggplot(sub4, aes(x= Syn5, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn1+Syn5)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = -1, option = "C") +
  geom_text(data=subset(sub4, ((Syn1+Syn5)/2)<=250), aes(label = Compound.Name), size = 2)

ggsave("Syn5_Syn1_AUC_AvgPotency.png", height = 6, width = 6)

ggplot(sub4, aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=(Syn1+Syn6)/2)) + 
  coord_fixed() +
  scale_color_viridis(direction = -1, option = "C") +
  geom_text(data=subset(sub4, ((Syn1+Syn6)/2)<=250), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_AUC_AvgPotency.png", height = 6, width = 6)

```

```{r, eval=FALSE, include=FALSE}
intersect(intersect(filter(sub4, Syn1/Syn5>1.25)$Compound.Name, filter(sub4, Syn1/Syn6>1.25)$Compound.Name), filter(sub4, HS12/HS01>1.25)$Compound.Name)

```

```{r}
x<-synGet("syn8533491")@filePath
preddat<-read.table(x, sep = '\t', header = TRUE, fill = TRUE) %>% filter(Supplier == "MIPE") %>%  dplyr::select(Hypergeo_pval, Supplier_ID)

colnames(preddat) <- c("pval", "Sample.ID")
preddat <- full_join(drugdat, preddat)
```

```{r}
sub3 <- dplyr::select(preddat, Cell.Line, Log.AC50.uM, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, Log.AC50.uM)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn5, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("AC50")
  #geom_text(data=subset(sub4, Syn1/Syn5>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn5_Syn1_AC50_Selectivity.png", height = 6, width = 6)


sub3 <- dplyr::select(preddat, Cell.Line, AUC.Fit, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, AUC.Fit)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn5, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("AUC")
  #geom_text(data=subset(sub4, Syn1/Syn5>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn5_Syn1_AUC_Selectivity.png", height = 6, width = 6)


sub3 <- dplyr::select(preddat, Cell.Line, Max.Resp, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, Max.Resp)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn5, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("Max Response")
  #geom_text(data=subset(sub4, Syn1/Syn5>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn5_Syn1_MaxResp_Selectivity.png", height = 6, width = 6)
```

```{r}
x<-synGet("syn8533698")@filePath
preddat<-read.table(x, sep = '\t', header = TRUE, fill = TRUE) %>% filter(Supplier == "MIPE") %>%  dplyr::select(Hypergeo_pval, Supplier_ID)

colnames(preddat) <- c("pval", "Sample.ID")
preddat <- full_join(drugdat, preddat)
```

```{r}
sub3 <- dplyr::select(preddat, Cell.Line, Log.AC50.uM, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, Log.AC50.uM)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("AC50")
  #geom_text(data=subset(sub4, Syn1/Syn6>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_AC50_Selectivity.png", height = 6, width = 6)


sub3 <- dplyr::select(preddat, Cell.Line, AUC.Fit, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, AUC.Fit)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("AUC")
  #geom_text(data=subset(sub4, Syn1/Syn6>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_AUC_Selectivity.png", height = 6, width = 6)


sub3 <- dplyr::select(preddat, Cell.Line, Max.Resp, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, Max.Resp)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("Max Response")
  #geom_text(data=subset(sub4, Syn1/Syn6>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_MaxResp_Selectivity.png", height = 6, width = 6)
```


```{r}
x<-synGet("syn8533696")@filePath
preddat<-read.table(x, sep = '\t', header = TRUE, fill = TRUE) %>% filter(Supplier == "MIPE") %>%  dplyr::select(Hypergeo_pval, Supplier_ID)

colnames(preddat) <- c("pval", "Sample.ID")
preddat <- full_join(drugdat, preddat)
```

```{r}
sub3 <- dplyr::select(preddat, Cell.Line, Log.AC50.uM, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, Log.AC50.uM)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("AC50")
  #geom_text(data=subset(sub4, Syn1/Syn6>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_AC50_Selectivity.png", height = 6, width = 6)


sub3 <- dplyr::select(preddat, Cell.Line, AUC.Fit, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, AUC.Fit)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("AUC")
  #geom_text(data=subset(sub4, Syn1/Syn6>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_AUC_Selectivity.png", height = 6, width = 6)


sub3 <- dplyr::select(preddat, Cell.Line, Max.Resp, Compound.Name, pval)
sub4 <- sub3 %>% 
  group_by(Compound.Name) %>% 
  nest() %>% 
  mutate(num_cells = map(data, nrow)) %>% 
  filter(num_cells == 6) %>% 
  mutate(data = map(data, function(x) {
    spread(x, Cell.Line, Max.Resp)
  })) %>% 
  unnest(data)

ggplot(sub4 %>% filter(!is.na(pval)), aes(x= Syn6, y=Syn1)) +
  geom_point(stat = "identity", aes(color=pval<0.05)) + 
  coord_fixed() +
  scale_color_manual(name = "mHG<0.05", values = setNames(c("red3", "green2"), c(F,T))) +
  geom_abline(slope=1, intercept=0) +
  ggtitle("Max Response")
  #geom_text(data=subset(sub4, Syn1/Syn6>=1.5), aes(label = Compound.Name), size = 2)

ggsave("Syn6_Syn1_MaxResp_Selectivity.png", height = 6, width = 6)
```